Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Clarify the vertical component of the mean velocity field

Normalized weighted averages for each recovery term at $x/D=1$ are computed and
multiplied by the cross-sectional area of the measurement plane, or the channel
width in the 2-D cases. Results are shown in a bar chart in
Figure~\ref{fig:br-cfd-recovery}. Consistent with the relatively large Reynolds
number regime, viscous transport is essentially negligible compared with other
mechanisms. Cross-stream advection---or the tendency of streamlines to diverge
and reduce the streamwise momentum---produces a negative effect for all cases,
though the 3-D SST model predicts significantly lower values. Vertical advection
is by definition zero for the 2-D cases. The 3-D cases show varying
results---with the SST model overpredicting and SA underpredicting the vertical
velocity's effect on replenishing streamwise momentum.

@@

Both the SST and SA models did a good job predicting the mean velocity field at
one turbine diameter downstream, but the SST model was more effective at
predicting turbulence kinetic energy, since it is solved for in the turbulence
model equations. Streamwise momentum recovery terms were computed from the CFD
results over an entire cross-section of the domain at $x/D=1$. Values for
transport due to the mean pressure gradient and turbulent fluctuations varied a
lot between the two turbulence models. Both models, however, we able to at least
qualitatively resolve the vertical velocity field, which will be crucial to
predicting the performance of closely spaced CFTs.

>>>>

Normalized weighted averages for each recovery term at $x/D=1$ are computed and
multiplied by the cross-sectional area of the measurement plane, or the channel
width in the 2-D cases. Results are shown in a bar chart in
Figure~\ref{fig:br-cfd-recovery}. Consistent with the relatively large Reynolds
number regime, viscous transport is essentially negligible compared with other
mechanisms. Cross-stream advection---or the tendency of streamlines to diverge
and reduce the streamwise momentum---produces a negative effect for all cases,
though the 3-D SST model predicts significantly lower values. Vertical advection
is by definition zero for the 2-D cases. The 3-D cases show varying
results---with the SST model overpredicting and SA underpredicting the vertical
velocity's effect on replenishing streamwise momentum. Nevertheless, both 3-D
models were able to qualitatively resolve this mean vertical advection caused by
blade tip vortex shedding, which will be crucial to predicting overall wake
recovery and the performance of closely spaced turbines.

@@

Both the SST and SA models did a good job predicting the mean velocity field at
one turbine diameter downstream, but the SST model was more effective at
predicting turbulence kinetic energy, since it is solved for in the turbulence
model equations. Streamwise momentum recovery terms were computed from the CFD
results over an entire cross-section of the domain at $x/D=1$. Values for
transport due to the mean pressure gradient and turbulent fluctuations varied a
lot between the two turbulence models. Both models, however, were able to at
least qualitatively resolve the vertical component of the near-wake's mean
velocity field, which will be crucial to predicting the performance of closely
spaced CFTs.
